### 2020-10-15 priority-gv.tex
Update priority-gv.tex

\subsubsection*{Operational Semantics}
Priority GV terms are evaluated as part of a configuration of processes. Configurations are defined by the following grammar:
\[
\begin{array}[t]{lcl}
    \tm{\conf{C}}, \tm{\conf{D}}, \tm{\conf{E}}
  & \Coloneqq & \tm{\phi\;M}
    \sep        \tm{\ppar{\conf{C}}{\conf{D}}}
    \sep        \tm{\res{x}{x'}{\conf{C}}}
  \\
  \tm{\phi}
  & \Coloneqq & \tm{\main}
    \sep        \tm{\child}
\end{array}
\]
Configurations ($\tm{\conf{C}}$, $\tm{\conf{D}}$, $\tm{\conf{E}}$) consist of threads $\tm{\phi\;M}$, parallel compositions $\tm{\ppar{\conf{C}}{\conf{D}}}$, and name restrictions $\tm{\res{x}{x'}{\conf{C}}}$. To preserve the functional nature of PGV, where programs return a single value, we use flags ($\tm{\phi}$) to differentiate between the main thread, marked $\tm{\main}$, and child threads created by $\tm{\spawn}$, marked $\tm{\child}$. Only the main thread returns a value. We determine the flag of a configuration by combining the flags of all threads in that configuration:
\[
  \tm{\main}  + \tm{\child} = \tm{\main}
  \quad
  \tm{\child} + \tm{\main}  = \tm{\main}
  \quad
  \tm{\child} + \tm{\child} = \tm{\child}
  \quad
  (\tm{\main}  + \tm{\main} \; \text{is undefined})
\]
Values ($\tm{V}$, $\tm{W}$), evaluation contexts ($\tm{E}$), thread evaluation contexts ($\tm{\conf{F}}$), and configuration contexts ($\tm{\conf{G}}$) are defined by the following grammars:
\[
\begin{array}[t]{lcl}
  \tm{V}, \tm{W}
  & \Coloneqq & \tm{x}
    \sep        \tm{K}
    \sep        \tm{\lambda x.M}
    \sep        \tm{\unit}
    \sep        \tm{\pair{V}{W}}
    \sep        \tm{\inl{V}}
    \sep        \tm{\inr{V}}
  \\
  \tm{E}
  & \Coloneqq & \tm{\hole} \\
  & \sep      & \tm{E\;M}
    \sep        \tm{V\;E} \\
  & \sep      & \tm{\letunit{E}{N}} \\
  & \sep      & \tm{\pair{E}{M}}
    \sep        \tm{\pair{V}{E}}
    \sep        \tm{\letpair{x}{y}{E}{M}} \\
  & \sep      & \tm{\inl{E}}
    \sep        \tm{\inr{E}}
    \sep        \tm{\casesum{E}{x}{M}{y}{N}} \\
  & \sep      & \tm{\absurd{E}}
  \\
  \tm{\conf{F}}
  & \Coloneqq & \tm{\phi\;E}
  \\
  \tm{\conf{G}}
  & \Coloneqq & \tm{\hole}
    \sep        \tm{\ppar{\conf{G}}{\conf{C}}}
    \sep        \tm{\res{x}{y}{\conf{G}}}
\end{array}
\]
We factor the reduction relation of PGV into a deterministic reduction on terms ($\tred$) and a non-deterministic reduction on configurations ($\cred$), see \cref{fig:pgv-operational-semantics}. We write $\tred^+$ and $\cred^+$ for the transitive closures, and $\tred^\star$ and $\cred^\star$ for the reflexive-transitive closures.

>>>>

\subsubsection*{Operational Semantics}

Priority GV terms are evaluated as part of a configuration of processes. Configurations are defined by the following grammar:
\[
\begin{array}[t]{lcl}
    \tm{\conf{C}}, \tm{\conf{D}}, \tm{\conf{E}}
  & \Coloneqq & \tm{\phi\;M}
    \sep        \tm{\ppar{\conf{C}}{\conf{D}}}
    \sep        \tm{\res{x}{x'}{\conf{C}}}
  \\
  \tm{\phi}
  & \Coloneqq & \tm{\main}
    \sep        \tm{\child}
\end{array}
\]
Configurations ($\tm{\conf{C}}$, $\tm{\conf{D}}$, $\tm{\conf{E}}$) consist of threads $\tm{\phi\;M}$, parallel compositions $\tm{\ppar{\conf{C}}{\conf{D}}}$, and name restrictions $\tm{\res{x}{x'}{\conf{C}}}$. To preserve the functional nature of PGV, where programs return a single value, we use flags ($\tm{\phi}$) to differentiate between the main thread, marked $\tm{\main}$, and child threads created by $\tm{\spawn}$, marked $\tm{\child}$. Only the main thread returns a value. We determine the flag of a configuration by combining the flags of all threads in that configuration:
\[
  \tm{\main}  + \tm{\child} = \tm{\main}
  \quad
  \tm{\child} + \tm{\main}  = \tm{\main}
  \quad
  \tm{\child} + \tm{\child} = \tm{\child}
  \quad
  (\tm{\main}  + \tm{\main} \; \text{is undefined})
\]
Values ($\tm{V}$, $\tm{W}$), evaluation contexts ($\tm{E}$), thread evaluation contexts ($\tm{\conf{F}}$), and configuration contexts ($\tm{\conf{G}}$) are defined by the following grammars:
\[
\begin{array}[t]{lcl}
  \tm{V}, \tm{W}
  & \Coloneqq & \tm{x}
    \sep        \tm{K}
    \sep        \tm{\lambda x.M}
    \sep        \tm{\unit}
    \sep        \tm{\pair{V}{W}}
    \sep        \tm{\inl{V}}
    \sep        \tm{\inr{V}}
  \\
  \tm{E}
  & \Coloneqq & \tm{\hole} \\
  & \sep      & \tm{E\;M}
    \sep        \tm{V\;E} \\
  & \sep      & \tm{\letunit{E}{N}} \\
  & \sep      & \tm{\pair{E}{M}}
    \sep        \tm{\pair{V}{E}}
    \sep        \tm{\letpair{x}{y}{E}{M}} \\
  & \sep      & \tm{\inl{E}}
    \sep        \tm{\inr{E}}
    \sep        \tm{\casesum{E}{x}{M}{y}{N}} \\
  & \sep      & \tm{\absurd{E}}
  \\
  \tm{\conf{F}}
  & \Coloneqq & \tm{\phi\;E}
  \\
  \tm{\conf{G}}
  & \Coloneqq & \tm{\hole}
    \sep        \tm{\ppar{\conf{G}}{\conf{C}}}
    \sep        \tm{\res{x}{y}{\conf{G}}}
\end{array}
\]

We factor the reduction relation of PGV into a deterministic reduction on terms ($\tred$) and a non-deterministic reduction on configurations ($\cred$), see \cref{fig:pgv-operational-semantics}. We write $\tred^+$ and $\cred^+$ for the transitive closures, and $\tred^\star$ and $\cred^\star$ for the reflexive-transitive closures.
